Analyzing the Impact of Bank of Canada's Monetary Policy on Consumer Debt

### 2024-04-20 paper/paper.qmd
updated files

---
title: "Impact of Bank of Canada's Monetary Policy on Consumer Debt Levels"
author: 
  - Abdul Ahad Qureshi
thanks: "Code and data are available at: https://github.com/abdulahadq29/debt."
date: today
date-format: long
abstract: "This analysis investigates the relationship between changes in the Bank of Canada's interest rate policy and consumer debt levels in Canada. Using a dataset of quarterly financial flows and stocks of household credit market debt, the impact of short-term interest rates on credit market debt to disposable income is examined. A linear regression model showed an inverse relationship between short-term interest rates and consumer debt levels. This analysis helps us in understanding the role of fiscal tools in shaping consumer financial behavior."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# References

>>>>

---
title: "Analyzing the Impact of Bank of Canada's Monetary Policy on Consumer Debt"
author: 
  - Abdul Ahad Qureshi
thanks: "Code and data are available at: https://github.com/abdulahadq29/debt."
date: today
date-format: long
abstract: "This analysis investigates the relationship between changes in the Bank of Canada's interest rate policy and consumer debt levels in Canada. Using a dataset of quarterly financial flows and stocks of household credit market debt, the impact of short-term interest rates on credit market debt to disposable income is examined. A linear regression model showed an inverse relationship between short-term interest rates and consumer debt levels. This analysis helps us in understanding the role of fiscal tools in shaping consumer financial behavior."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

\newpage
# References
